---
title: "Maximum slides per week"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{maxslidesperweek}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# In which Week happended the most slides

- Use the iffi-data to find out in which week the most events happened

- We use the data that already comes with the `iffitoR`-package

- first we load the packages

```{r setup, message=F, warning=F}
library(iffitoR)
library(lubridate)
library(stringr)
library(leaflet.extras)
library(sf)
library(leaflet)
library(dplyr)
library(ggplot2)
library(glue)
library(forcats)
```

- now we load the iffi-data (it is actually already loaded)

```{r}
data_iffi = landsld
glimpse(data_iffi)
```
- the data that comes with the package is already pre-processed. Meaning it has the classification-columns in english and some computed day-columns

# Max Slides per Day 

- We yet dont have the data agggregated per week, so lets have a look which day was the day with the most slides

```{r}
data_iffi %>% 
  filter(str_detect(second_level, "translational")) %>% 
  count(date, sort=T)
```
- On the 21st June of 2007 9 slides happened which is the max number of slides 


## Visualize the max slides per day

```{r maxdayviz, fig.width=7, fig.height=7}
dat = data_iffi %>% 
  filter(date == as.Date("2007-06-21")) %>% 
  st_transform(4326)


# the color palette for the categorical data 
cf = colorFactor(palette = "RdYlBu", domain=dat$second_level)
sl = unique(dat$second_level)

map = leaflet(dat) %>%
  addProviderTiles(providers$Stamen.TonerLite) 

for (g in sl) {
  d = dat %>% filter(second_level == g)
  map = map %>% addCircles(
    data = d,
    popup = paste0("date: ", d$date, "<br>", "type:", d$second_level),
    color =  ~ cf(d$second_level),
    group = g
  )
}

map %>% addLayersControl(overlayGroups = sl) 

```

***

# Aggregate per week

```{r}
data_iffi %>% 
  filter(date_info == "day") %>% 
  filter(str_detect(second_level, "translational")) %>% 
  mutate(week = paste0(year.int, formatC(week(date), flag=0, width=2))) %>% 
  count(week, sort=T) %>% 
  mutate(first_day_of_week = as.Date(paste0(week, 1), "%Y%U%u")) %>% 
  mutate(week = glue("{week}  ({n})")) %>% 
  mutate(week = fct_reorder(week, n)) %>% 
  mutate(ishighlight = ifelse(n == 9, TRUE, FALSE)) %>% 
  head(n = 12) %>% 
  ggplot() +
  geom_col(aes(x=n, y=week, fill=ishighlight)) +
  scale_fill_manual(values = c("grey", "darkred"), guide=F) +
  theme_light() +
  labs(x = "# of events per week",
       y = "Week",
       title = "Weeks with highest number of Slides")
```

